\input{./common.tex}

\title{Введение в GNU/Linux}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% Begin Document  %%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{frame}
	\frametitle{Bash scripting. Advanced.}
	\titlepage
	\vspace{-0.5cm}
	\begin{center}
	%\frontpagelogo
	\end{center}
\end{frame}


\begin{frame}
	\tableofcontents
	[hideallsubsections]
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%   
%%%%%%%%%% Content starts here %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Manipulate the different I/O streams  with I/O Redirection}
\mode<all>{\input{../../slides/bash/redirection/frame1.tex}}
\mode<all>{\input{../../slides/cmdline/pipes.tex}}
\mode<all>{\input{../../slides/cmdline/io-redirection.tex}}
\mode<all>{\input{../../slides/cmdline/io-redirection-usecases.tex}}
%\mode<all>{\input{../../slides/bash/redirection/frame2.tex}}
%\mode<all>{\input{../../slides/bash/redirection/frame3.tex}}
%\mode<all>{\input{../../slides/bash/redirection/frame4.tex}}

%\mode<all>{\input{../../slides/bash/runtime/frame3.tex}}
\section{Repeat operations with loops.}
\mode<all>{\input{../../slides/bash/loops/frame1.tex}}

%\mode<all>{\input{../../slides/bash/loops/frame2.tex}}

\mode<all>{\input{../../slides/bash/loops/frame3.tex}}
\mode<all>{\input{../../slides/bash/loops/frame4.tex}}
\mode<all>{\input{../../slides/bash/loops/frame5.tex}}
\mode<all>{\input{../../slides/bash/loops/frame6.tex}}
%\mode<all>{\input{../../slides/bash/loops/frame7.tex}}
% while
\mode<all>{\input{../../slides/bash/loops/frame8.tex}}
\mode<all>{\input{../../slides/bash/loops/frame9.tex}}
%\mode<all>{\input{../../slides/bash/loops/frame11.tex}}
%IFS
\mode<all>{\input{../../slides/bash/bashsams/frame31.tex}}
\mode<all>{\input{../../slides/bash/loops/frame11_1.tex}}
\mode<all>{\input{../../slides/bash/loops/frame12.tex}}
%\mode<all>{\input{../../slides/bash/loops/frame13.tex}}
%

\mode<all>{\input{../../slides/bash/loops/frame10_1.tex}}

\section{Group pieces of code.}
% subshell
%\mode<all>{\input{../../slides/bash/runtime/frame10}}
% functions
\mode<all>{\input{../../slides/bash/functions/frame1}}
\mode<all>{\input{../../slides/bash/functions/frame2}}
%\mode<all>{\input{../../slides/bash/functions/frame3}}
% example
\mode<all>{\input{../../slides/bash/functions/frame4}}
\mode<all>{\input{../../slides/bash/functions/frame5}}
\mode<all>{\input{../../slides/bash/functions/frame6}}
%\mode<all>{\input{../../slides/bash/functions/frame7}}


\section{Expansions cont.}
% tilde expansion
\mode<all>{\input{../../slides/bash/runtime/tildeexp.tex}}
%command expansion
\mode<all>{\input{../../slides/bash/runtime/frame7.tex}}
%comments
\mode<all>{\input{../../slides/bash/runtime/frame1.tex}}

% example && || chain
\section{ if alternatives.}
\mode<all>{\input{../../slides/bash/tests/frame8_1_usage.tex}}
\mode<all>{\input{../../slides/bash/tests/frame8_2_usage.tex}}
% case
\mode<all>{\input{../../slides/bash/tests/frame8.tex}}

\section{Debugging scripts.}
\mode<all>{\input{../../slides/bash/debug/frame1}}
\mode<all>{\input{../../slides/bash/debug/frame2}}
% debug variables
\mode<all>{\input{../../slides/bash/debug/frame3}}
\mode<all>{\input{../../slides/bash/debug/frame4}}
% TODO 2 things in one. typical errors in conditions
% directory script   filetype file
% ./filetype 
% ./filetype "file 1"
%common conditional operator errors
\mode<all>{\input{../../slides/bash/tests/frame6.tex}}
%\mode<all>{\input{../../slides/bash/tests/frame7.tex}}
\mode<all>{\input{../../slides/bash/debug/frame5}}

\section{Command types.}
\mode<all>{\input{../../slides/cmdline/shell-intro/frame6_cmd_types.tex}}
\mode<all>{\input{../../slides/cmdline/shell-intro/frame5_task_cmd_types.tex}}
\mode<all>{\input{../../slides/bash/branching/frame2.tex}}

\end{document}
